### 2016-02-02 Projects/DelCo_2012/Report/DelCo_2012.tex
minor edit to CAF paper

\begin{tabbing}
\hspace{1.5in} \= \\
ESTC \> Delaware County Emergency Services Training Center \\
MCFRS \> Montgomery County (MD) Fire and Rescue Service \\
NIST \> National Institute of Standards and Technology \\
TFT \> Task Force Tips \\
\end{tabbing}

>>>>

\begin{tabbing}
\hspace{1.5in} \= \\
CAF \> Compressed Air Foam \\
ESTC \> Delaware County Emergency Services Training Center \\
MCFRS \> Montgomery County (MD) Fire and Rescue Service \\
NIST \> National Institute of Standards and Technology \\
TFT \> Task Force Tips \\
\end{tabbing}
